### 2011-08-01 doc/theses/svirec/kap1.tex
fixing

Nowadays, one of the most largely used standards for information representation and data exchange on the Internet is the eXtensible Markup Language (XML) \cite{xml}. While XML as a markup language provides syntactic flexibility, the structure of an XML document is described with a so-called XML schema language. The two most popular XML schema languages proposed by W3C are Document Type Definition (DTD) \cite{xml} and XML Schema Definition (XSD) \cite{xsd1,xsd2,xsd3}. They support some kind of semantic content (e.g., keys and foreign keys), but for improvement of semantic expressiveness XML integrity constraints for XML \cite{ic} have been defined.

However, similarly to the problem of schemas also problem of detection of integrity constrains has two distinct aspects. First, if integrity constraints are not explicitly expressed, they need to be detected from the given set of data. Second, if integrity constraints are expressed, XML document may not be consistent with respect to them and this needs to be detected (checking the satisfaction of integrity constraint in an XML document). Moreover, detected XML data inconsistency needs to be repaired. We choose this very aspect of detection of integrity constraints along with the repair of the inconsistent XML document. Since several different classes of integrity constraints have been defined for XML, we choose functional dependency (FD) \cite{fd}, which is the most common semantic constraint used in relational databases.

@@

As we mention before, we focus on the detection of XML data inconsistency with respect to the functional dependency and consequential repairing this violation. The aim of the thesis is to propose an algorithm repairing XML functional dependency violations for a given XML document and a set of functional dependencies. It analyses recent approaches and discusses their advantages and disadvantages. The focus of the thesis is to incorporate the weight model and to involve the user into the process of finding and applying the repair and find out how this interaction helps. A part of this thesis is an experimental implementation of the proposed algorithm and its experimental evaluation.

@@

Chapter 2 introduces basic definitions which are necessary for further chapters. Chapter 3 presents recent approaches of repairing XML functional dependency violations. In Chapter 4 is the main algorithm of this thesis proposed. Chapter 5 contains details of the experimental implementation. Experimental result are presented in Chapter 6. Finally, Chapter 7 contains a conclusion and several suggestions for future work.

>>>>

Nowadays, one of the most largely used standards for information representation and data exchange on the Internet is the eXtensible Markup Language (XML) \cite{xml}. While XML as a markup language provides syntactic flexibility, the structure of an XML document is described with a so-called XML schema language. The two most popular XML schema languages proposed by W3C\footnote{The World Wide Web Consorcium, \url{http://www.w3.org}} are Document Type Definition (DTD) \cite{xml} and XML Schema Definition (XSD) \cite{xsd1,xsd2,xsd3}. They support some kind of semantic content (e.g., keys and foreign keys), but for improvement of semantic expressiveness integrity constraints for XML \cite{ic} have been defined.

However, similarly to the problem of schemas, also the problem of detection of integrity constrains has two distinct aspects. First, if integrity constraints are not explicitly expressed, they need to be detected from the given set of data. Second, if integrity constraints are expressed, XML document may not be consistent with respect to them and this needs to be detected (checking the satisfaction of integrity constraint in an XML document). Moreover, the detected XML data inconsistency needs to be repaired. In this thesis we choose the latter aspect of detection of integrity constraints along with the repair of the inconsistent XML document. Since several different classes of integrity constraints have been defined for XML, we choose so-called functional dependency (FD) \cite{fd} which is the most common semantic constraint used in relational databases.

@@

The aim of this thesis is to propose an algorithm repairing XML functional dependency violations for a given XML document and a set of functional dependencies. It analyses recent approaches and discusses their advantages and disadvantages. The focus of the thesis is to incorporate a weight model, to involve the user the process of finding and applying the repair and to find out how this interaction helps. An important part of the thesis is an experimental implementation of the proposed algorithm and its experimental evaluation.

@@

Chapter 2 introduces basic definitions which are necessary for further chapters. Chapter 3 presents recent approaches of repairing XML functional dependency violations. In Chapter 4 the main algorithm is proposed. Chapter 5 contains details of the experimental implementation. Experimental result are presented in Chapter 6. Finally, Chapter 7 contains a conclusion and several suggestions for future work.

### 2011-08-01 doc/theses/svirec/kap5.tex
fixing

A part of this work is experimental implementation of our proposed algorithm. Besides our approach, we have also implementened the algorithm proposed in \cite{RepAndConsistentAnswer}, to be able to compare it with our algorithm. Our algorithm has been implemented in the Java language in the version 6.0 as a part of the schema inference framework for XML jInfer \cite{jinfer}.

@@

jInfer framework was developed as a Software Project at the Faculty of Mathematics and Physics, Charles University at Prague. The framework is based on NetBeans platform and is mainly used for XML schema inference. Although our proposed algorithm is not dealing with the schema inference, jInfer is designed to be extensible and is suitable for incorporation our algorithm into it.

>>>>

A part of this work is an experimental implementation of our proposed algorithm. Besides our approach, we have also implementened the algorithm proposed in \cite{RepAndConsistentAnswer}, to be able to compare it with our algorithm. Our algorithm has been implemented in the Java language, version 6.0 as a part of the schema inference framework for XML called jInfer \cite{jinfer}.

@@

jInfer framework was developed as a Software Project at the Faculty of Mathematics and Physics, Charles University at Prague. The framework is based on the NetBeans platform and is mainly used for XML schema inference. Although our proposed algorithm is not dealing with schema inference, jInfer is designed to be extensible and is suitable for incorporation of our algorithm.
